Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex

%Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

@@

\subsection{Risk and Benefit Rankings} 
When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}). We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.

>>>>

%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

@@

\subsection{Risk and Benefit Rankings}

When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}). We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.
